---
title: "Week 2 lab exercises"
format: gfm
editor: visual
---

**Question 1**

```{r}
knitr::opts_chunk$set(warning=FALSE, message = FALSE)

library(tidyverse)

psy_stat <- read_csv("https://uoepsy.github.io/data/surveydata_historical.csv")
```

**Q2**

There are `r nrow(filter(psy_stat, birthmonth == "jul"))` students born in July like me.

**Q3**

```{r}
psy_stat <- psy_stat |>
  mutate(taller = height > 182)

head(psy_stat)
```

**Q4**

Of those who reported their height `r sum(psy_stat$taller, na.rm = T) / sum(psy_stat$height > 0, na.rm = T) *100` % are taller than 182

**Q5**

```{r}
psy_stat |>
  summarise(
    mean = mean(height, na.rm = T),
    sd = sd(height, na.rm = T)
  )
```

**Q6**

```{r}
 ggplot(psy_stat, aes(x = height))+
  geom_histogram(fill = "grey", color = "black", na.rm = T) +
  labs(x= "Height in cm", y = "Frequency", title = "Figure 1")+
  theme_minimal()
```

**Q7**

```{r}
psy_stat |>
  group_by(course) |>
  summarise(
    mean = mean(height, na.rm = T),
    sd = sd(height, na.rm = T)
  )
```

**Q8**

```{r}
 ggplot(psy_stat, aes(x = height))+
  geom_histogram(fill = "grey", color = "black", na.rm = T) +
  facet_wrap(~course)+
  labs(x= "Height in cm", y = "Frequency", title = "Figure 1")+
  theme_minimal()
```

**Q9** There are `r sum(is.na(psy_stat$height))` missing data points for height

**Q10** There are `r sum(psy_stat$height > 173, na.rm = T)` students taller than me. That is, `r sum(psy_stat$height > 173, na.rm = T) / (nrow(psy_stat) - sum(is.na(psy_stat$height)))*100` %.

**Q11**

```{r}
sleep_qual <- psy_stat |>
  filter(course == "usmr" & year == 2022 & is.na(sleeprating) == F)
```

**Q12**

```{r}
sum <- sleep_qual |>
  summarise(
    mean = mean(sleeprating),
    sd = sd(sleeprating),
    n = n()
  )

sum
```

**Q13** The boundaries of a 95 % confidence interval of the mean sleep rating (`r sum$mean`) is `r sum$mean -1.96*(sum$sd/sqrt(sum$n))` and `r sum$mean + 1.96*(sum$sd/sqrt(sum$n))`
