---
title: "Week 1"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(patchwork)
library(ggcats)

pets <- read_csv("https://uoepsy.github.io/data/pets_seattle.csv")
```

**Question 1-2**

```{r}
summary(pets)
head(pets)
```

**Question 3**

Pet 47 is called `r pets$animals_name[47]`

Pet 200 is called `r pets$animals_name[200]`

**Question 4**

```{r}
dogs <- pets %>% filter(species == "Dog")
cats <- pets %>% filter(species == "Cat")
```

**Question 5**

The weight of the heaviest cat is `r max(cats\$weight_kg)`. The lightest dog weighs `r min(dogs$weight_kg)`.

**Question 6** There are `nrow(pets %>% filter(species != "Cat" & species != "Dog"))` that are not dogs. They are both of the species `rlevels(as.factor(filter(pets, species != "Cat" & species != "Dog")$species))`.

**Question 7**

```{r}
pets <- pets %>%
  mutate(round_weight = round(weight_kg,0))
```

**Question 8**

```{r}
summary(pets)
```

**Question 9**

```{r}
dice <- function(num = 1) {
  sum(sample(1:6, num, replace=TRUE))
}
```

**Question 11**

```{r}
dx20 <- replicate(20, dice())
```

**Question 12**

```{r}
hist(dx20)
```

**Question 13**

```{r}
d <- data.frame(dx20 = dx20,
                dx100 =replicate(100, dice()),
               dx1000 = replicate(1000, dice())) %>% pivot_longer(cols = c(dx20,dx100,dx1000), names_to = "n", values_to = "dice", names_prefix = "dx")

p1<-ggplot(d, aes(x=dice, fill = n)) +
  geom_bar() +
  facet_wrap(~n) 

p1
```

**Question 14**

```{r}
wdice <- function(num = 1){
    sum(sample(1:6, num, replace=TRUE, prob = c(0.15,0.15,0.15,0.15,0.15,0.25)))
}

wd <- data.frame(wdx20 = replicate(20,wdice()),
                 wdx100 = replicate(100, wdice()),
                 wdx1000 = replicate(1000, wdice())) %>% pivot_longer(cols = c(wdx20,wdx100,wdx1000), names_to = "n", values_to = "dice", names_prefix = "wdx")

p2<- ggplot(wd, aes(x=dice, fill = n)) +
  geom_bar() +
  facet_wrap(~n)

p1/p2
```

**Question 15**

```{r}
wdice <- function(num = 1){
    sum(sample(1:6, num, replace=TRUE, prob = c(0.15,0.15,0.15,0.15,0.15,0.5)))
}

wd2 <- data.frame(wd2x20 = replicate(20,wdice()),
                 wd2x100 = replicate(100, wdice()),
                 wd2x1000 = replicate(1000, wdice())) %>% pivot_longer(cols = c(wd2x20,wd2x100,wd2x1000), names_to = "n", values_to = "dice", names_prefix = "wd2x")

p3<- ggplot(wd2, aes(x=dice, fill = n)) +
  geom_bar() +
  facet_wrap(~n)

p1/p2/p3
```
